---
pagetitle: MBAt Hang
format:
  html:
    include-in-header:
      text: |
        <style>        
        .resources-list {
        color: red
        }
        .resource {
        color: blue
        }
        </style>
---

# MBAt Hang: Your Alumni & Student Hub 
### for Master of Business Analytics at Monash University

Welcome to MBAt Hang, the central gathering place for current students and alumni of the Business Analytics Masters program. This platform is built to strengthen community ties, celebrate achievements, and keep everyone informed about upcoming opportunities. Whether you're a recent graduate looking to stay connected or a current student seeking guidance, this space is designed to help you grow, collaborate, and stay in the loop.

# Upcoming Events

🎓 Alumni Networking Night
Date: March 14, 2025
Location: University Atrium
Reconnect with your cohort, meet new graduates, and build relationships with professionals across a wide range of industries.

💡 Career Pathways Panel
Date: April 2, 2025
Location: Learning Theatre 3
Hear alumni share their career journeys, challenges, and advice for carving your path after graduation.

🧠 Research Spotlight Showcase
Date: May 20, 2025
Location: Innovation Hub
Current students present their capstone and thesis projects to alumni, faculty, and peers in a friendly exhibition-style event.

🎉 Annual Community Dinner
Date: June 8, 2025
Location: Grand Hall
A celebratory evening bringing together students, alumni, and faculty for food, stories, and recognition of outstanding contributions.

```{r}
#| echo: false
#| warning: false
#| message: false
# remotes::install_github("cynthiahqy/ggtilecal")
library(ggtilecal)
library(dplyr)
library(tibble)
library(lubridate)
library(yaml)
library(ggplot2)
library(ggiraph)
library(reactable)

## for YAML collections
yaml_date_nodes_to_tbl <- function(list) {
  list |>
    lapply(as.data.frame) |>
    dplyr::bind_rows() |>
    tibble::as_tibble()
}

## for data frames
tidy_date_tbl <- function(df) {
  df |>
    dplyr::mutate(across(ends_with("Date"), ~ lubridate::ymd(.x))) |>
    dplyr::mutate(endDate = dplyr::coalesce(endDate, startDate)) |>
    dplyr::arrange(startDate)
}

verify_date_df <- function(df) {
  assertr::verify(df, startDate <= endDate)
}

tidy_date_df_export <- function(df) {
  df |>
    dplyr::mutate(
      startDate = format(startDate, "%Y-%m-%d"),
      endDate = format(endDate, "%Y-%m-%d")
    )
}

write_yaml_col_maj_FALSE <- function(x, file) {
  write_yaml(x, file, column.major = FALSE)
}

plot_calendar <- function(tbl) {
  tbl |>
    gg_facet_wrap_months(unit_date) +
    geom_text(
      aes(label = emoji),
      nudge_y = -0.25,
      nudge_x = -0.1,
      size = 3.5,
      na.rm = TRUE
    ) +
    geom_tile_interactive(
      aes(
        tooltip = paste(
          details |> tidyr::replace_na(""),
          ifelse(is.na(details), "", "@"),
          room |> tidyr::replace_na("")
        ),
        data_id = id
      ),
      alpha = 0.2,
      fill = "transparent",
      colour = "grey80"
    )
}

render_calendar <- function(yaml_file) {
  read_yaml(yaml_file) |>
    yaml_date_nodes_to_tbl() |>
    tidy_date_tbl() |>
    verify_date_df() |>
    dplyr::mutate(id = row_number()) |>
    dplyr::relocate(id, .before = details) |>
    reframe_events(startDate, endDate) |>
    plot_calendar()
}
```

### Current schedule {#sec-current-schedule}

:::: {.panel-tabset}

### Calendar View

```{r}
#| echo: false
#| output: true
ggiraph::girafe(
  ggobj = render_calendar(here::here("events/2025_schedule.yaml"))
)
```

### Detailed View

```{r}
#| echo: false
#| output: true
read_yaml(here::here("events/2025_schedule.yaml")) |>
  yaml_date_nodes_to_tbl() |>
  tidy_date_tbl() |>
  verify_date_df() |>
  dplyr::mutate(id = row_number()) |>
  dplyr::relocate(id, .before = details) |>
  reframe_events(startDate, endDate) |>
  select(unit_date, event = details, start = startTime, end = endTime, room) |>
  reactable(
    columns = list(
      unit_date = colDef(name = "Date"),
      event = colDef(name = "Topic"),
      start = colDef(name = "From"),
      end = colDef(name = "End"),
      room = colDef(name = "Room")
    )
  )
```

::::

# Resources for students

:::{.resources-list}
:::{.resource}
Unit Guide
:::
:::{.resource}
Course Map
:::
:::

# Connect with us

Want to connect with current and past MBAt Students? Send an email to [Krisanat.Anukarnsakulchularp@monash.edu](mailto:Krisanat.Anukarnsakulchularp@monash.edu]) to join the official discord server
